Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-28 beap_pres_dec2022/beap_pres_dec.tex
nov 28, midnight updates to beap_pres, almost done

	\footnotetext[3]{\tiny\cite{levinson1987slipped,sehn2015insertions}}	
	\end{frame}

@@

@@

@@

	% Blocks frame
	\section{Blocks in Beamer}
	\begin{frame}{Blocks in Beamer}
		\begin{block}{Standard Block}
			This is a standard block.
		\end{block}
		\begin{alertblock}{Alert Message}
			This block presents alert message.
		\end{alertblock}
		\begin{exampleblock}{An example of typesetting tool}
			Example: MS Word, \LaTeX{}
		\end{exampleblock}
	\end{frame}

>>>>

	\footnotetext[3]{\tiny\cite{mirkin2007expandable}}	
	\end{frame}

@@

	\textbf{Bayesian Statistics: Model-based statistical inference}

	\begin{figure}

		\begin{equation} \tag{1}
			p(D|\theta)
		\end{equation}
	\caption{\textit{Likelihood}} \pause

		\begin{equation} \tag{2}
			p(\theta|D)
		\end{equation}
	\caption{\textit{Posterior}}

	\end{figure}

@@

	\uncover<1>{
	\begin{itemize}
		\item The increasing complexity and magnitude of available data can make the likelihood difficult to calculate   \newline
	\end{itemize}

	\begin{figure}
	\scalebox{2}{
		$ p(D|\theta)$}
	\end{figure}} \pause

	\uncover<2>{
	\begin{figure}
		\vspace{-1.5cm}
		\scalebox{2}{
			$ p(D|\theta)$}
	\end{figure}

	\begin{tikzpicture}[remember picture,overlay]
		\node at (current page.center) {\includegraphics[width=5cm]{no.png}};
	\end{tikzpicture}

	\begin{figure}
		\vspace{1.5cm}
	\begin{itemize}
		\item Calculation of the likelihood is replaced with a simulation step
	\end{itemize}
	\end{figure}}

@@

	% Blocks frame
	%\section{Blocks in Beamer}
	%\begin{frame}{Blocks in Beamer}
	%	\begin{block}{Standard Block}
	%		This is a standard block.
	%	\end{block}
	%	\begin{alertblock}{Alert Message}
	%		This block presents alert message.
	%	\end{alertblock}
	%	\begin{exampleblock}{An example of typesetting tool}
	%	\end{exampleblock}
	%\end{frame}
